Real-world Feasibility Analysis of ACT Algorithm for Robotic Manipulation on Home

### 2025-05-18 paper.tex
fix:参考文献修改
fix:参考文献内容修改替换

\newcolumntype{C}{>{\centering\arraybackslash}X} % 定义居中列类型
\usepackage{cleveref}
\crefformat{figure}{\textbf{Figure~#2#1#3}}

@@

%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
\titlerunning{Real-world Feasibility Analysis of ACT Algorithm for Robotic Manipulation}  % 页眉显示的短标题
\author{
  Junlin Huang\inst{1} \and
  Feihong Liu\inst{1} \and
  Siyu Wang\inst{1} \and
  Yang Yang\inst{1} \and
  Yuhang Li\inst{1} \and
  Qiuyue Che\inst{1} \and
  Qiushuang Liu\inst{1} \and
  Deping Li\inst{1}\thanks{Corresponding author}  % 标记通讯作者
}

@@

\institute{
  Jinan University, \\
  Zhuhai, China \\
  \email{lideping@jnu.edu.cn}  % 优先展示通讯作者邮箱 \\  % 如果会议允许只放一个邮箱
  %\email{gzhuangjunlin@163.com}  
}
\maketitle

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{fig3.pdf}
\caption{leader arm (Left) and follower arm(right).} \label{fig2-1}
\end{figure}

@@

\begin{figure}
\centering
  \includegraphics[width=0.95\textwidth]{fig4.pdf}
  \caption{ initial state(upper left); target state(upper right);training environment(bottom).} \label{fig2}
  \end{figure}

@@

This task optimized the positioning of the wrist-mounted vision system. As shown in Fig.~\ref{fig12}, the initial configuration (Position 1) exhibited tier recognition errors in multi-layered disc scenarios, primarily manifesting as erroneous grasps of second-layer discs with only a 40\% success rate. The wrist-mounted camera is crucial for precision operations~\cite{ref6}.By relocating the camera to the robotic gripper's center position (Position 2), precise tier recognition was achieved, significantly improving the grasping success rate to 90\%.

@@

\section{Acknowledgments}
This research was supported by the National College Student Innovation and Entrepreneurship Training Program of China under project numbers 202410559078 and 202310559124.

@@

%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
\bibliographystyle{unsrt}
\bibliography{ref}
%
\end{document}

>>>>

\newcolumntype{C}{>{\centering\arraybackslash}X} % 定义居中列类型
\usepackage{cleveref}
\crefformat{figure}{\textbf{Fig.~#2#1#3}}

@@

%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
\titlerunning{Real-world Feasibility Analysis of ACT Algorithm for Robotic Manipulation}  % 页眉显示的短标题
\author{
  Junlin Huang\inst{1} \and
  Feihong Liu\inst{1} \and
  Siyu Wang\inst{1} \and
  Yang Yang\inst{1} \and
  Yuhang Li\inst{1} \and
  Qiuyue Che\inst{1} \and
  Qiushuang Liu\inst{1} \and
  Deping Li\inst{1}\thanks{Corresponding author: lideping@jnu.edu.cn}
}

@@

\institute{
  School of Intelligent Systems Science and Engineering/JNU-Industry School of Artificial Intelligence,   % 补充学院名称
  Jinan University, 
  Zhuhai 519070, China \\ % 补充邮编
  \email{lideping@jnu.edu.cn}  % 明确标记通讯作者邮箱
  %\email{gzhuangjunlin@163.com}  
}

\maketitle

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{fig3.pdf}
\caption{Leader arm (Left) and follower arm(right).} \label{fig2-1}
\end{figure}

@@

\begin{figure}
\centering
  \includegraphics[width=0.95\textwidth]{fig4.pdf}
  \caption{ Initial state(upper left); target state(upper right);training environment(bottom).} \label{fig2}
  \end{figure}

@@

\noindent This task optimized the positioning of the wrist-mounted vision system. As shown in Fig.~\ref{fig12}, the initial configuration (Position 1) exhibited tier recognition errors in multi-layered disc scenarios, primarily manifesting as erroneous grasps of second-layer discs with only a 40\% success rate. The wrist-mounted camera is crucial for precision operations~\cite{ref6}.By relocating the camera to the robotic gripper's center position (Position 2), precise tier recognition was achieved, significantly improving the grasping success rate to 90\%.

@@

\subsubsection{Acknowledgments} This research was supported by the National College Student Innovation and Entrepreneurship Training Program of China under project numbers 202410559078 and 202310559124.

@@

%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
\bibliographystyle{splncs04}
\bibliography{ref}
%
\end{document}
